Capstone Movielens Report

### 2025-06-04 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
Matrix Factorization: Helper functions described.

### MF: Helper Funtions

>>>>

### MF: Helper Functions

#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
\

::: { #func.mf.residual.dataframe.params.description .sidebar }
##### Description
\

Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.

##### Parameters
\

###### ***train_set***
\

::: { #func.mf.residual.dataframe.params.train_set .sidebar }
The dataset to be trained.
:::

##### Source Code
\

The folowing is the source code of the function:
```{r eval=FALSE}
mf.residual.dataframe <- function(train_set){
  train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(rglr.UMGY_effect, by='year') |>
    left_join(rglr.UMGYD_effect, by='days') |>
    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
    select(userId, movieId, rsdl)
}
```

::: {.noteblock data-latex=""}
The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
:::

##### Return
\

A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.params.description) above for the details).

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
\

This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.

##### Parameters
\

::: { #func.UMGYDE_model.predict.params.test_set .sidebar }
###### ***test_set***
\

The dataset for testing the _UMGYDE Model_ after it has been fully trained.
:::

##### Source Code
\

The following is the source code of the function:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
:::

##### Return
\

A data frame object containing predicted values.
